A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
Add proper x and y axis labels

```{r cluster_clusters, warning=FALSE}
clusters <-
   unique(slim_PM_dat[c("cluster_1", "cluster_2", "cluster_3")])

@@

```{r plot_disease_pressure}
slimmer_PM_dat %>%
   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
   geom_boxplot()
```

>>>>

```{r cluster_clusters}
clusters <-
   unique(slim_PM_dat[c("cluster_1", "cluster_2", "cluster_3")])

@@

```{r plot_disease_pressure}
slimmer_PM_dat %>%
   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
   geom_boxplot() +
   xlab("Disease pressure") +
   ylab("Grain yield (t/ha)")
```
